---
title: "getting_data"
author: "olivier"
date: "3/18/2022"
output: html_document
---

The goal is to get all tracks and train stations off the [Amtrack network](https://en.wikipedia.org/wiki/List_of_Amtrak_routes) and the first step is getting data.

First step is collecting data about Amtrack. I went with a csv without coordinates because at this point we do not need them. I have tuned the request in overpass api then used cURL. 

```{bash}
curl --globoff -o relation_amtrack.csv "http://overpass-api.de/api/interpreter?data=[out:csv(::type,::id,name)];rel[network="Amtrak"];out;"
```

Cleaning the csv

```{r}
relations_amtrack <- read.csv("../Data/relation_amtrack.csv", sep = "\t")
# we can drop relation and clean names
names(relations_amtrack) <- c("rel", "id", "name")
relations_amtrack <- relations_amtrack[, c("id", "name")]      
```

We just need the one with `=`

```{r}
relations_amtrack <- relations_amtrack[grep(pattern = "=", relations_amtrack$name),]
```

Better but we are still facing some trouble:

- we have potential duplicates: see `Amtrak Keystone Service: Harrisburg => Philadelphia` 

- we have two way: see `Seattle => Chicago` and `Chicago => Seattle`

We need to understand why:

```{r}
relations_amtrack$id[relations_amtrack$name =="Amtrak Keystone Service: Harrisburg => Philadelphia"]
```

I have done a quick check using `https://www.openstreetmap.org/relation/11914034` changing at the end of the url the id of the relation and it look like you get a different number of train stations for each (or different one). 

rel(id:11914036);
(._;>;);
out count;